### 2019-12-12 README.Rmd
paper out

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Territoriality and the organization of technology during the Last Glacial Maximum in southwestern Europe"

@@

This repository contains the data and code for our paper:

> Cascalheira, J. (2019). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "Territoriality and the organization of technology during the Last Glacial Maximum in southwestern Europe"

@@

This repository contains the data and code for the paper:

> Cascalheira, J. (2019). _`r Title`_. PLOS ONE 14(12): e0225828 <https://doi.org/10.1371/journal.pone.0225828>

The pre-print is online here:
